Clean spectral data

### 2020-11-04 R/clean_spectral_data.Rmd
decreased fig height to make them fit on 1 page each

# save figure to file
ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 9, height = 12)
```

@@

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 12)
```

>>>>

# save figure to file
ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 9, height = 10)
```

@@

# save figure to file
ggsave(filename = here::here("analysis","figures", "spectra_per_species.pdf"), width = 10, height = 10)
```
